---
title: "Shiny Course Project"
author: "John Tribbia"
date: "10/15/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Overview
  
#### This presentation contains documentation for the Texas House Sale Price interactive plot application. The application can be found [**here**](https://johntribbia.shinyapps.io/shiny-app-reproducible-research/)

## Data Used. 
####- This application plots median home sale price in Texas cities using the `txhousing` data set and allows the user to choose what city or cities they want to view on the plot.  
####- This data set contains the information about home sales of 46 Texas cities between 2000 and 2015 with 10 variables:
  
```{r data, echo = FALSE,message=FALSE, warning=FALSE}
library(ggplot2)
data("txhousing")
```

```{r echo=FALSE}
str(txhousing)
```

## Shiny files. 
  
### The application is built using Shiny package. The source code can be found in 2 files:  
####- `ui.R`. 
####- `server.R`. 
  
### Both files can be found here: [GitHub repo](https://github.com/johntribbia/shiny-app-reproducible-research)
